SAT Competition 2020\tnoteref{title}

### 2021-01-18 paper/main.tex
table and solver-name formatting

\begin{abstract}
The SAT Competitions constitute a well-established series of yearly open international competitive algorithm implementation competitions
focusing on the Boolean satisfiability (or propositional satisfiability, SAT) problem. 
In this article, we provide
a detailed account on the 2020 instantiation of the SAT Competition, including the 
 new competition tracks and benchmark selection procedures, overview of solving strategies implemented in top-performing solvers, 
and a more detailed analysis of the empirical data obtained from running the competition.
%SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
%This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
%Another novelty was the application-specific sub-track of the main track, 
%where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
%We used new tools to select and distribute benchmark instances and their attributes. 
%In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
%It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
\end{abstract}

@@

The rest of this article is organized as follows. TODO -MJ

===

OLD:

In Section~\ref{sec:overview}, we start with an overview of the competition,
including detailed description of the competition tracks and their purpose,
the general rules and the used computing environment.
Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.

OLD END ===

\section{Overview of the Competition}
\label{sec:overview}

@@

\section{Description of Benchmark Instances}
\label{sec:instances}

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
By this rule solver authors are required to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.

@@

To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unknown result. 
Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).

@@

\begin{table}
\caption{Main ALL}
\label{tab:mainALL}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
1     & 3926.2 & 264 & {\bf Kissat-sat} \\
(1)   & 4083.1 & 260 & Kissat \\
2     & 4179.3 & 253 & {\bf Relaxed\_newTech} \\
3     & 4266.7 & 248 & {\bf CMS-ccnr-lsids} \\
(3)   & 4278.0 & 250 & CMS-ccnr \\
      & 4428.1 & 250 & CaDiCaL-alluip-trail \\
      & 4429.6 & 250 & CaDiCaL-alluip \\
      & 4436.5 & 245 & Relaxed \\
      & 4501.2 & 243 & CMS-walksat \\
      & 4554.0 & 243 & CaDiCaL-trail \\
      & 4560.0 & 238 & Kissat-unsat \\
      & 4607.6 & 246 & CaDiCaL-sc2020 \\
      & 5157.7 & 216 & Undominated \\
      & 5159.6 & 220 & f2trc-DL \\
      & 5177.0 & 214 & PADC\_DL \\              
\end{tabular}
\end{table}

\begin{table}
\caption{Main SAT}
\label{tab:mainSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & CMS-ccnr \\
      & 3355.5 & 143 & Relaxed \\
      & 3721.2 & 139 & CMS-walksat \\
      & 3830.5 & 134 & Kissat \\
      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
      & 3909.6 & 135 & CaDiCaL-alluip \\
      & 4265.6 & 126 & CaDiCaL-trail \\
      & 4368.6 & 130 & CaDiCaL-sc2020 \\
   & 4804.9 & 114 & Kissat-unsat \\
   & 5173.2 & 110 & Undominated \\
   & 5244.1 & 107 & PADC\_DL \\
   & 5264.9 & 110 & f2trc-DL \\           
\end{tabular}
\end{table}

\begin{table}
\caption{Main UNSAT}
\label{tab:mainUNSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
1     & 4315.1 & 124 & {\bf Kissat-unsat} \\
(1)   & 4335.6 & 126 & Kissat \\
(1)   & 4724.8 & 118 & Kissat-sat \\
 2    & 4842.5 & 117 & {\bf CaDiCaL-trail} \\
--    & 4846.7 & 116 & CaDiCaL-sc2020 \\
(2)   & 4947.8 & 115 & CaDiCaL-alluip-trail \\
(2)   & 4949.6 & 115 & CaDiCaL-alluip \\
 3    & 4991.4 & 110 & {\bf f2trc-s} \\
(3)   & 5051.4 & 109 & f2trc \\
(3)   & 5054.3 & 110 & f2trc-DL \\
      & 5069.6 & 109 & Maple\_Mix \\
      & 5110.0 & 107 & PADC\_DL \\
      & 5126.9 & 107 & Maple\_Simp \\
      & 5128.9 & 107 & MapleCBT-DL-v3 \\
      & 5142.2 & 106 & Undominated \\      
\end{tabular}
\end{table}

\begin{table}
\caption{Planning (ALL)}
\label{tab:planning}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & CMS-ccnr \\
(2)   & 6472.9 & 79 & CMS-walksat \\
 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
      & 6650.1 & 79 & CaDiCaL-trail \\
      & 6713.0 & 75 & Maple\_Mix \\
      & 6746.5 & 75 & MapleCOMSPS\_init \\
      & 6754.3 & 73 & Maple\_Simp \\
      & 6773.0 & 73 & MapleCOMSPS\_drup \\
      & 6773.9 & 73 & Kissat-sat \\
      & 6774.2 & 73 & Kissat \\
      & 7025.5 & 68 & upGlucose3.0\_PADC \\
      & 7044.7 & 66 & Glucose3.0\_proofs \\
\end{tabular}
\end{table}

\begin{table}
\caption{Parallel (ALL)}
\label{tab:parallelALL}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 3316.6 & 283 & {\bf pmcompspsthirty} \\
(1)& 3714.7 & 271 & pmcompspsixty \\
 2 & 3743.4 & 269 & {\bf plingeling} \\
 3 & 3985.3 & 260 & {\bf manyglucosethirty} \\
   & 4022.7 & 262 & painlessmaplevone \\
   & 4036.3 & 258 & manyglucosesixty \\
   & 4103.3 & 260 & painlessmaplevtwo \\
   & 4433.3 & 243 & syrupscavel \\
   & 4903.4 & 225 & treengeling \\
   & 5240.1 & 213 & abcdsatptwenty \\
\end{tabular}
\end{table}

\begin{table}
\caption{Parallel (SAT)}
\label{tab:parallelSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2853.7 & 153 & {\bf pmcompspsthirty} \\
 2 & 2913.6 & 154 & {\bf painlessmaplevone} \\
(2)& 3082.7 & 151 & painlessmaplevtwo \\
(1)& 3196.9 & 148 & pmcompspsixty \\
 3 & 3805.9 & 133 & {\bf plingeling} \\
   & 4048.3 & 130 & manyglucosesixty \\
   & 4076.2 & 130 & manyglucosethirty \\
   & 4675.4 & 119 & syrupscavel \\
   & 4907.1 & 114 & treengeling \\
   & 6337.5 & \phantom{0}85 & abcdsatptwenty \\
\end{tabular}
\end{table}

\begin{table}
\caption{Parallel (UNS)}
\label{tab:parallelUNS}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 3680.8 & 136 & {\bf plingeling} \\
 2 & 3779.5 & 130 & {\bf pmcompspsthirty} \\
 3 & 3894.3 & 130 & {\bf manyglucosethirty} \\
(3)& 4024.2 & 128 & manyglucosesixty \\
   & 4142.8 & 128 & abcdsatptwenty \\
   & 4191.1 & 124 & syrupscavel \\
   & 4232.5 & 123 & pmcompspsixty \\
   & 4899.8 & 111 & treengeling \\
   & 5123.9 & 109 & painlessmaplevtwo \\
   & 5131.9 & 108 & painlessmaplevone \\
\end{tabular}
\end{table}

\begin{table}
\caption{Claud (ALL)}
\label{tab:claud}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2603.8 & 299 & {\bf mallobecs} \\
 2 & 3146.8 & 278 & {\bf toposat} \\
 3 & 4797.6 & 213 & {\bf slime} \\
   & 6800.8 & 132 & paracooba \\
   & 7299.0 & 110 & ctsat \\
   & 8468.3 & \phantom{0}62 & paracoobamarch \\
\end{tabular}
\end{table}

@@

\subsection{Observations}

@@

\begin{table}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 316. 
There were 48 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
46 & 11.5 & Kissat-unsat \\
39 & \phantom{0}9.8 & Kissat-sat \\
26 & \phantom{0}6.5 & Kissat \\
18 & \phantom{0}4.5 & CMS-ccnr-lsids \\
14 & \phantom{0}3.5 & MapleCM+dist+sat2s \\
13 & \phantom{0}3.2 & Relaxed \\
13 & \phantom{0}3.2 & Maple-alluip-trail \\
12 & \phantom{0}3.0 & upGlucose3.0\_PADC \\
10 & \phantom{0}2.5 & CMS-ccnr \\
10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
131.5 & 32.9 & Kissat-sat \\
122.6 & 30.6 & Kissat \\
115.4 & 28.9 & Kissat-unsat \\
\phantom{0}92.3 & 23.1 & CMS-ccnr-lsids \\
\phantom{0}88.8 & 22.2 & CMS-ccnr \\
\phantom{0}84.1 & 21.0 & CaDiCaL-alluip-trail \\
\phantom{0}84.0 & 21.0 & CaDiCaL-alluip \\
\phantom{0}83.0 & 20.7 & CaDiCaL-sc2020 \\
\phantom{0}82.3 & 20.6 & Relaxed\_newTech \\
\phantom{0}81.5 & 20.4 & Relaxed \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
13.0 & 3.3 & Kissat \\
11.9 & 3.0 & Kissat-unsat \\
11.7 & 2.9 & Relaxed\_newTech \\
11.4 & 2.8 & Kissat-sat \\
10.8 & 2.7 & CaDiCaL-alluip-trail \\
10.8 & 2.7 & CaDiCaL-alluip \\
10.5 & 2.6 & Relaxed \\
10.4 & 2.6 & CaDiCaL-sc2020 \\
10.3 & 2.6 & CMS-walksat \\
\phantom{0}9.6 & 2.4 & CaDiCaL-trail \\
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{VBS metrics for the results of the Main track, SAT instances. 
The total number of solved problems was 182. 
There were 48 (non-disqualified) participating solvers.
Each table always shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainSAT}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
29 & 15.9 & Kissat-sat \\
16 & \phantom{0}8.8 & Kissat \\
14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
10 & \phantom{0}5.5 & Relaxed \\
\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
70.1 & 38.5 & Kissat-sat \\
48.6 & 26.7 & Kissat \\
45.2 & 24.8 & CMS-ccnr-lsids \\
43.4 & 23.8 & Relaxed\_newTech \\
42.4 & 23.3 & CMS-ccnr \\
41.6 & 22.8 & Relaxed \\
34.7 & 19.0 & CaDiCaL-alluip-trail \\
34.6 & 19.0 & CaDiCaL-alluip \\
33.7 & 18.5 & CMS-walksat \\
32.8 & 18.0 & CaDiCaL-sc2020 \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
9.3 & 5.1 & Relaxed\_newTech \\
8.1 & 4.4 & Relaxed \\
7.8 & 4.3 & CMS-walksat \\
7.0 & 3.8 & Kissat-sat \\
6.7 & 3.7 & Kissat \\
6.7 & 3.7 & CMS-ccnr \\
6.6 & 3.6 & CMS-ccnr-lsids \\
6.2 & 3.4 & CaDiCaL-sc2020 \\
6.2 & 3.4 & CaDiCaL-alluip-trail \\
6.2 & 3.4 & CaDiCaL-alluip \\
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{abstract}
The SAT Competitions constitute a well-established series of yearly open international algorithm implementation competitions
focusing on the Boolean satisfiability (or propositional satisfiability, SAT) problem. 
In this article, we provide
a detailed account on the 2020 instantiation of the SAT Competition, including the 
 new competition tracks and benchmark selection procedures, overview of solving strategies implemented in top-performing solvers, 
and a more detailed analysis of the empirical data obtained from running the competition.
%SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
%This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
%Another novelty was the application-specific sub-track of the main track, 
%where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
%We used new tools to select and distribute benchmark instances and their attributes. 
%In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
%It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
\end{abstract}

@@

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
the solving strategies implemented distinctly in  top-ranking  solvers. 
Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.
\todo{Need to decide on final structure regardign the results overview and analysis}

\section{Overview of SAT Competition 2020}
\label{sec:overview}

@@

\section{Benchmarks}
\label{sec:instances}

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.

@@

To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result. 
Furthermore, we made sure not to select instances of families which are already represented in the set of newly submitted instances and moreover excluded random, agile and planning instances (due to the Planning track).

@@

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
(1)   & 4083.1 & 260 & \solver{Kissat} \\
2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
      & 4436.5 & 245 & \solver{Relaxed} \\
      & 4501.2 & 243 & \solver{CMS-walksat} \\
      & 4554.0 & 243 & \solver{CaDiCaL-trail} \\
      & 4560.0 & 238 & \solver{Kissat-unsat} \\
      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
      & 5157.7 & 216 & \solver{Undominated} \\
      & 5159.6 & 220 & \solver{f2trc-DL} \\
      & 5177.0 & 214 & \solver{PADC-DL} \\              
\end{tabular}
\caption{Main ALL}
\label{tab:mainALL}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1    & 2997.4 & 150 & \solbert{Relaxed\_newTech} \\
 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
      & 3355.5 & 143 & \solver{Relaxed} \\
      & 3721.2 & 139 & \solver{CMS-walksat} \\
      & 3830.5 & 134 & \solver{Kissat} \\
      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
      & 4265.6 & 126 & \solver{CaDiCaL-trail} \\
      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
   & 4804.9 & 114 & \solver{Kissat-unsat} \\
   & 5173.2 & 110 & \solver{Undominated} \\
   & 5244.1 & 107 & \solver{PADC-DL} \\
   & 5264.9 & 110 & \solver{f2trc-DL} \\           
\end{tabular}
\caption{Main SAT}
\label{tab:mainSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline   
1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
(1)   & 4335.6 & 126 & \solver{Kissat} \\
(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
--    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
(3)   & 5051.4 & 109 & \solver{f2trc} \\
(3)   & 5054.3 & 110 & \solver{f2trc-DL} \\
      & 5069.6 & 109 & \solver{Maple-Mix} \\
      & 5110.0 & 107 & \solver{PADC-DL} \\
      & 5126.9 & 107 & \solver{Maple-Simp} \\
      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
      & 5142.2 & 106 & \solver{Undominated} \\      
\end{tabular}
\caption{Main UNSAT}
\label{tab:mainUNSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline   
 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
      & 6713.0 & 75 & \solver{Maple-Mix} \\
      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
      & 6754.3 & 73 & \solver{Maple-Simp} \\
      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
      & 6773.9 & 73 & \solver{Kissat-sat} \\
      & 6774.2 & 73 & \solver{Kissat} \\
      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
\end{tabular}
\caption{Planning (ALL)}
\label{tab:planning}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-STR-32} \\
(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-STR-64} \\
 2 & 3743.4 & 269 & \solbert{Plingeling} \\
 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
   & 4903.4 & 225 & \solver{Treengeling} \\
   & 5240.1 & 213 & \solver{abcdsat-p20} \\
\end{tabular}
\caption{Parallel (ALL)}
\label{tab:parallelALL}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-STR-32} \\
 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
-- & 3196.9 & 148 & \solver{Painless-MCOMSPS-STR-64} \\
 3 & 3805.9 & 133 & \solbert{Plingeling} \\
   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
   & 4907.1 & 114 & \solver{Treengeling} \\
   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
\end{tabular}
\caption{Parallel (SAT)}
\label{tab:parallelSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 3680.8 & 136 & \solbert{Plingeling} \\
 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-STR-32} \\
 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
   & 4142.8 & 128 & \solver{abcdsat-p20} \\
   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
   & 4232.5 & 123 & \solver{Painless-MCOMSPS-STR-64} \\
   & 4899.8 & 111 & \solver{Treengeling} \\
   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
   & 5131.9 & 108 & \solver{Painless-Maple-v1} \\
\end{tabular}
\caption{Parallel (UNSAT)}
\label{tab:parallelUNS}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
 3 & 4797.6 & 213 & \solbert{Slime} \\
   & 6800.8 & 132 & \solver{Paracooba} \\
   & 7299.0 & 110 & \solver{CTsat} \\
   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
\end{tabular}
\caption{Cloud (ALL)}
\label{tab:cloud}
\end{table}

@@

@@

\begin{table}
\centering
\begin{tabular}{ccl}
\bf VBS1 & \bf Percent Total & \bf Solver \\
\hline
46 & 11.5 & \solver{Kissat-unsat} \\
39 & \phantom{0}9.8 & \solver{Kissat-sat} \\
26 & \phantom{0}6.5 & \solver{Kissat} \\
18 & \phantom{0}4.5 & \solver{CMS-ccnr-lsids} \\
14 & \phantom{0}3.5 & \solver{MapleCM+dist+sat2s} \\
13 & \phantom{0}3.2 & \solver{Relaxed} \\
13 & \phantom{0}3.2 & \solver{Maple-alluip-trail} \\
12 & \phantom{0}3.0 & \solver{upGlucose3.0-PADC} \\
10 & \phantom{0}2.5 & \solver{CMS-ccnr} \\
10 & \phantom{0}2.5 & \solver{CaDiCaL-sc2020} \\
\end{tabular}
~\\[1em]
\begin{tabular}{ccl}
\bf VBS2 & \bf Percent Total & \bf Solver \\
\hline
131.5 & 32.9 & \solver{Kissat-sat} \\
122.6 & 30.6 & \solver{Kissat} \\
115.4 & 28.9 & \solver{Kissat-unsat} \\
\phantom{0}92.3 & 23.1 & \solver{CMS-ccnr-lsids} \\
\phantom{0}88.8 & 22.2 & \solver{CMS-ccnr} \\
\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-trail} \\
\phantom{0}84.0 & 21.0 & \solver{CaDiCaL-alluip} \\
\phantom{0}83.0 & 20.7 & \solver{CaDiCaL-sc2020} \\
\phantom{0}82.3 & 20.6 & \solver{Relaxed-newTech} \\
\phantom{0}81.5 & 20.4 & \solver{Relaxed} \\
\end{tabular}
~\\[1em]
\begin{tabular}{ccl}
\bf VBS3 & \bf Percent Total & \bf Solver \\
\hline
13.0 & 3.3 & \solver{Kissat} \\
11.9 & 3.0 & \solver{Kissat-unsat} \\
11.7 & 2.9 & \solver{Relaxed-newTech} \\
11.4 & 2.8 & \solver{Kissat-sat} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip-trail} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip} \\
10.5 & 2.6 & \solver{Relaxed} \\
10.4 & 2.6 & \solver{CaDiCaL-sc2020} \\
10.3 & 2.6 & \solver{CMS-walksat} \\
\phantom{0}9.6 & 2.4 & \solver{CaDiCaL-trail} \\
\end{tabular}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 316. 
There were 48 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\end{table}

%\begin{table}
%\caption{VBS metrics for the results of the Main track, SAT instances. 
%The total number of solved problems was 182. 
%There were 48 (non-disqualified) participating solvers.
%Each table always shows the first ten solvers sorted according to the respective metric.}
%\label{tab:vbsMainSAT}
%\begin{center}
%\begin{tabular}{ccl}
%VBS1 & percent total & solver \\
%\hline
%29 & 15.9 & Kissat-sat \\
%16 & \phantom{0}8.8 & Kissat \\
%14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
%12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
%10 & \phantom{0}5.5 & Relaxed \\
%\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
%\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
%\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
%\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
%\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
%\end{tabular}
%\end{center}
%\begin{center}
%\begin{tabular}{ccl}
%VBS2 & percent total & solver \\
%\hline
%70.1 & 38.5 & Kissat-sat \\
%48.6 & 26.7 & Kissat \\
%45.2 & 24.8 & CMS-ccnr-lsids \\
%43.4 & 23.8 & Relaxed\_newTech \\
%42.4 & 23.3 & CMS-ccnr \\
%41.6 & 22.8 & Relaxed \\
%34.7 & 19.0 & CaDiCaL-alluip-trail \\
%34.6 & 19.0 & CaDiCaL-alluip \\
%33.7 & 18.5 & CMS-walksat \\
%32.8 & 18.0 & CaDiCaL-sc2020 \\
%\end{tabular}
%\end{center}
%\begin{center}
%\begin{tabular}{ccl}
%VBS3 & percent total & solver \\
%\hline
%9.3 & 5.1 & Relaxed\_newTech \\
%8.1 & 4.4 & Relaxed \\
%7.8 & 4.3 & CMS-walksat \\
%7.0 & 3.8 & Kissat-sat \\
%6.7 & 3.7 & Kissat \\
%6.7 & 3.7 & CMS-ccnr \\
%6.6 & 3.6 & CMS-ccnr-lsids \\
%6.2 & 3.4 & CaDiCaL-sc2020 \\
%6.2 & 3.4 & CaDiCaL-alluip-trail \\
%6.2 & 3.4 & CaDiCaL-alluip \\
%\end{tabular}
%\end{center}
%\end{table}

%\begin{table}
%\caption{VBS metrics for the results of the Main track, UNSAT instances. 
%The total number of solved problems was 134. 
%There were 48 (non-disqualified) participating solvers.
%Each table always shows the first ten solvers sorted according to the respective metric.}
%\label{tab:vbsMainUNSAT}
%\begin{center}
%\begin{tabular}{ccl}
%VBS1 & percent total & solver \\
%\hline
%38 & 28.4 & Kissat-unsat \\
%11 & \phantom{0}8.2 & Maple-alluip-trail \\
%10 & \phantom{0}7.5 & Kissat \\
%10 & \phantom{0}7.5 & Kissat-sat \\
%\phantom{0}8 & \phantom{0}6.0 & MapleCMused+dist \\
%\phantom{0}7 & \phantom{0}5.2 & upGlucose3.0\_PADC \\
%\phantom{0}6 & \phantom{0}4.5 & CMS-ccnr-lsids \\
%\phantom{0}3 & \phantom{0}2.2 & f2trc \\
%\phantom{0}3 & \phantom{0}2.2 & Relaxed \\
%\phantom{0}3 & \phantom{0}2.2 & Glucose3.0\_proofs \\
%\end{tabular}
%\end{center}
%\begin{center}
%\begin{tabular}{ccl}
%VBS2 & percent total & solver \\
%\hline
%86.5 & 64.6 & Kissat-unsat \\
%74.0 & 55.2 & Kissat \\
%61.4 & 45.8 & Kissat-sat \\
%55.4 & 41.4 & f2trc-s \\
%55.2 & 41.2 & DurianSat \\
%53.6 & 40.0 & Maple-alluip-trail \\
%53.4 & 39.8 & f2trc \\
%52.4 & 39.1 & f2trc-DL \\
%51.8 & 38.6 & MapleCMused+dist \\
%51.7 & 38.6 & PADC\_DL \\
%\end{tabular}
%\end{center}
%\begin{center}
%\begin{tabular}{ccl}
%VBS3 & percent total & solver \\
%\hline
%6.7 & 5.0 & Kissat-unsat \\
%6.3 & 4.7 & Kissat \\
%4.7 & 3.5 & CaDiCaL-trail \\
%4.6 & 3.5 & CaDiCaL-alluip-trail \\
%4.6 & 3.5 & CaDiCaL-alluip \\
%4.4 & 3.3 & Kissat-sat \\
%4.3 & 3.2 & CaDiCaL-sc2020 \\
%3.5 & 2.6 & f2trc-s \\
%3.4 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
%3.1 & 2.3 & f2trc-DL \\
%\end{tabular}
%\end{center}
%\end{table}
%\todo{Probably hide tab:vbsMainSAT and tab:vbsMainUNSAT.}

Table~\ref{tab:vbsMainALL} renders the just described three metrics applied 
to the full results of the Main track. We can see that the respective leaderboards 
are generally dominated by \solver{Kissat} and its configurations.
VBS1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
in particular on \SI{11.5}{\percent} of all the solved instances.
